%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Classicthesis-Styled CV
% LaTeX Template
% Version 1.0 (22/2/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Alessandro Plasmati
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[oneside,fontsize=11.5pt]{scrartcl}%

\reversemarginpar % Move the margin to the left of the page 


\newcommand{\MarginText}[1]{\marginpar{\raggedleft\itshape\small#1}} % New command defining the margin text style

\usepackage[nochapters]{classicthesis} % Use the classicthesis style for the style of the document
\usepackage[LabelsAligned]{currvita} % Use the currvita style for the layout of the document


\renewcommand{\cvheadingfont}{\LARGE\color{Maroon}} % Font color of your name at the top

\usepackage{hyperref} % Required for adding links	and customizing them
\hypersetup{colorlinks, breaklinks, urlcolor=Blue, linkcolor=Blue} % Set link colors

\newlength{\datebox}\settowidth{\datebox}{September 2014} % Set the width of the date box in each block

\newcommand{\NewEntry}[3]{\noindent\hangindent=0em\hangafter=0 \parbox{\datebox}{\small \textit{#1}}\hspace{-1em} #2 #3 % Define a command for each new block - change spacing and font sizes here: #1 is the left margin, #2 is the italic date field and #3 is the position/employer/location field
\vspace{0.2em}} % Add some white space after each new entry

\newcommand{\Description}[1]{\hangindent=0em\hangafter=0\noindent\footnotesize{#1}\par\normalsize\vspace{1em}} % Define a command for descriptions of each entry - change spacing and font sizes here --

%George changes
\usepackage[left=4.5cm,right=2cm, top=2.2cm, bottom=2.2cm]{geometry}

\usepackage{xcolor}
\newcommand{\Sectiontitle}{\noindent\spacedlowsmallcaps}

%removed \raggedright after \noindent
%\pagenumbering{gobble}

%----------------------------------------------------------------------------------------

\begin{document}

\thispagestyle{empty} % Stop the page count at the bottom of the first page

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\begin{cv}{\spacedallcaps{George Kour}}\vspace{1.5em} % Your name


%\NewEntry{year of Birth}{1985} % Birthplace and date

\NewEntry{Address}{3 Simha Holzberg st., Tel-Aviv Jaffa, Israel}

\NewEntry{E-mail}{\href{mailto:kourgeorge@gmail.com}{kourgeorge@gmail.com}} % Email address

\NewEntry{Phone}{(M) 052-5808010} % Phone number(s)

\NewEntry{Website}{\href{kour.me}{kour.me}}

\NewEntry{Linked-In Page}{\href{http://il.linkedin.com/in/georgekour/}{http://il.linkedin.com/in/georgekour/}} % Personal website

\NewEntry{Researcher Page}{\href{http://researcher.ibm.com/researcher/view.php?person=ibm-GKOUR}{http://researcher.ibm.com/researcher/view.php?person=ibm-GKOUR}} % Personal website


\vspace{1.5em} % Extra white space between the personal information section and goal

%----------------------------------------------------------------------------------------
%	Goal
%----------------------------------------------------------------------------------------

%\noindent\spacedlowsmallcaps{Goal}\vspace{1em}

%\Description{I am looking for a half time academic position as a teaching assistant or a full/half research position in the field of machine learning and Big-Data analytics.}

%\vspace{1em}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------

\Sectiontitle{Work Experience}\vspace{0.5em}

\NewEntry{2017 -- Present}{Research Staff Member}

\Description{\MarginText{\textsc{IBM Research}}\textbf{Language and Conversation Group}\\
Our group study machine learning techniques, especially deep neural networks, for natural language processing application. 
The main goal of the group is conducting original and valuable research, publish papers at top tier conferences and transferring technologies to relevant business units.
As a researcher, I am involved in writing research proposal, implementing and training models for various discriminative and generative text related tasks.
In addition, I am a member of the AI Technologies Invention Developmnemt Board.
The goal of the board members is evaluate invention disclosures, help inventors fine-tune their ideas and decide what invetions are submitted as patent applications.
}

%------------------------------------------------

\NewEntry{2016 - 2018}{Co-Founder and Senior Researcher}

\Description{\MarginText{\textsc{Lofic}}\textbf{Lofic}\\
As a collaborative music recording platform Lofic uses AI technologies to redefine music creation.
My role in the team is to lead the company research efforts in the field of sound improvement. 
}


%------------------------------------------------

\NewEntry{2016 - 2020}{Lecturer - Junior Faculty Member}

\Description{\MarginText{\textsc{Haifa University}}\textbf{Sagol Department of Neurobiology}\\
I am a lecturer on scientific programming using MATLAB. 
The course is intended for neuroscience graduate students and its goal is to give introductory programming and problem-solving skills to enable researchers to exploit the power of computing in their research.
}

%------------------------------------------------

\NewEntry{2016 -- 2017}{Research Engineer}

\Description{\MarginText{\textsc{Hewlett Packard Enterprise Labs}}\textbf{Analytics Lab}\\
I was involved in several efforts in the lab including developing algorithms for Business Intelligence, clustering by intent and implementing deep neural networks for anomaly detection.
}

%------------------------------------------------

\NewEntry{2014 -- 2016}{Data Science Engineer}

\Description{\MarginText{\textsc{HP Software R\&D}}\textbf{Project: Predictive ALM}\\
As a technical lead of the predictive ALM team, I was responsible for implementing predictive capabilities on top of the data stored in HP application management line of products such as Application Lifecycle
Management (ALM), Agile Manager (AGM) and Modern Quality Management (MQM). 
}

%Reference: Bill \textsc{Lumbergh}\ \ +1 (000) 111 1111\ \ $\cdotp$\ \ \href{mailto:bill@initech.com}{bill@initech.com}}


%------------------------------------------------

\NewEntry{2009 -- 2014}{Software Developer}

\Description{\MarginText{\textsc{HP Software R\&D}}\textbf{Project: Application Lifecycle Management (ALM)}\\
ALM is a set of software products designed for accelerating the delivery of secure, reliable modern applications.
I was a member of the client infrastructure team that was responsible for the .Net desktop client platform of ALM. After two years in this position, I have moved to the web client infrastructure team developing the new web interface of ALM Angular.
}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\newpage

\Sectiontitle{Education}\vspace{0.5em}

\NewEntry{2016 -- Present}{Ph.D Candidate in Neurobiology}

\Description{\MarginText{\textsc{Haifa University}}\textsc{Sagol Department of Neurobioligy}\ \newline 
\textbf{Research Intent:} My research aim at elucidating the neural basis of the state representation in the brain.\\
\textbf{Advisor:} Dr.~Genela \textsc{Morris}}


\NewEntry{2011 -- 2014}{Master of Science in Electrical Engineering \textsc{(cum laude})}

\Description{\MarginText{\textsc{Tel-Aviv University}}\textsc{Faculty of Electrical Engineering}\ \ $\cdotp$\ \ \textbf{GPA:} 93.8\newline 
\textbf{Thesis Title:} \textit{Real-time Segmentation and Recognition of On-line Handwritten Arabic Script}\newline
\textbf{Description:} The thesis proposes an approach for segmenting Arabic handwritten strokes while being scribed using classification method based on a wavelet based approximation of the EMD metric. \newline
\textbf{Advisors:} Prof.~Dana \textsc{Ron} \& Dr.~Raid \textsc{Saabne}}

%------------------------------------------------


\NewEntry{2004 -- 2009}{Bachelor of Science in Computer Engineering}

\Description{\MarginText{\textsc{Technion - Israel Institute of Technology}}\textsc{Faculty of Computer Science}\ \ $\cdotp$\ \  \textbf{GPA}: 83.4 \newline
\textbf{Specialization:} \textit{Programming languages and Scientific Programming}\newline
\textbf{Description:} A four-year degree that run in conjunction with the department of Electrical Engineering.}

%------------------------------------------------

%\vspace{1em} % Extra space between major sections


%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------


\Sectiontitle{Publications}\vspace{0.5em}

\NewEntry{November 2020}{Balancing via Generation for Multi-Class Text Classification Improvement}

\Description{\textsc{Proceedings of the 2020 Conference on Empirical Methods in Natural Language Processing: Findings} 
\\
\textbf{Authors:} Naama Tepper, Esther Goldbraich, Naama Zwerdling, George Kour, Ateret Anaby Tavor, Boaz Carmeli}

%------------------------------------------------


\NewEntry{February 2020}{Do Not Have Enough Data? Deep Learning to the Rescue!}

\Description{\textsc{AAAI Conference on Artificial Intelligence} 
\\
\textbf{Authors:} Boaz Carmeli, George Kour, Naama Zwerdling, Amir Kantor, Naama Tepper, Segev Shlomov, Esther Goldrich}

%------------------------------------------------

\NewEntry{June 2019}{Evaluation Metrics for Generated Text Corpora}

\Description{\textsc{Conference on Empirical Methods in Natural Language Processing (Under Review)}
\\
\textbf{Authors:} Boaz Carmeli, Naama Zwerdling, George Kour, Inbal Ronen, Naama Tepper, Matan Eyal, Esther Goldrich}

%------------------------------------------------


\NewEntry{May 2019}{Neural Network Gradient-based Learning of Black-box Functions} 

\Description{\textsc{International Conference on Learning Representations}
\\
\textbf{Authors:} Alon Jacovi, Guy Hadash, Einat Kermany, Boaz Carmeli, Ofer Lavi, George Kour, Jonathan Berant}

%------------------------------------------------

\NewEntry{April 2019}{Estimating Attentional Set-Shifting in Varying Contextual Bandits} 

\Description{\textsc{A PrePrint on bioRxiv}
\\
\textbf{Authors:} George Kour, Genella Morris}

%------------------------------------------------
%\newpage
\NewEntry{March 2017}{An Algorithm for Handling Time Prediction of Software Defects} 

\Description{\textsc{International Conference on Computer Science and Information Technology}
\\
\textbf{Authors:} George Kour, Shaul Strachan, Raz Regev}

%------------------------------------------------
\NewEntry{September 2016}{Prediction-Based, Prioritized Market-Share Insight Extraction} 

\Description{\textsc{International Conference on Advanced Data Mining and Applications}
\\
\textbf{Authors:} Renato Keshet, Alina Maor, George Kour}

%------------------------------------------------

\NewEntry{September 2014}{Real-time Segmentation of On-line Handwritten Arabic Script}

\Description{\textsc{International Conference on Frontiers in Handwriting Recognition}
\\ 
\textbf{Authors}: George Kour, Raid Saabne}

%------------------------------------------------

\NewEntry{August 2014}{Fast Classification of Handwritten On-line Arabic Characters}

\Description{\textsc{International Conference of Soft Computing and Pattern Recognition}
\\
\textbf{Authors:} George Kour, Raid Saabne}


%----------------------------------------------------------------------------------------
%	PATENTS
%----------------------------------------------------------------------------------------
\vspace{1em}

\Sectiontitle{Patents} \vspace{0.5em}

\NewEntry{July 2020}{Removing unnecessary history from reinforcement learning state}

\Description{\textsc{United States patent application}, US20200210884A1.
\\
\textbf{Inventors:} Guy Hadash, Boaz Carmeli, George Kour}

\NewEntry{July 2020}{Deep learning testing}

\Description{\textsc{United States patent application}, US20200210848A1
\\
\textbf{Inventors:} George Kour, Guy Hadash, Yftah Ziser, Ofer Lavi, Guy Lev}


\NewEntry{March 2018}{Timing estimations for application lifecycle management work items determined through machine learning}

\Description{\textsc{Granted United States patent}, US10310852B2.
\\
\textbf{Inventors:}  Strachan Shaul, Kour George, Regev Raz}

\NewEntry{April 2017}{Using machine learning regression to estimate time for completing application lifecycle management work item}

\Description{\textsc{United States Patent Application}, US20180307998A1.
\\
\textbf{Inventors:}  Strachan Shaul, Kour George, Regev Raz}

\NewEntry{October 2016}{Quality prediction}

\Description{\textsc{Granted United States Patent}, US10354210B2.
\\
\textbf{Inventors:} Kour George, Toplian Yaniv, Vinik Alon}

%----------------------------------------------------------------------------------------
%	HONOURS and AWARDS
%----------------------------------------------------------------------------------------


\Sectiontitle{Special Activities, Honours \& Awards} \vspace{0.5em} 
\newlength{\langbox} % Create a new length for the length of languages to keep them equally spaced
\settowidth{\langbox}{January201} % Length equals the length of "English" - if you have a longer language in your list put it here

\Description{\MarginText{\textsc{IBM}}\parbox{\langbox}{October 2018}$\cdotp$\ \ \textbf{Member of the Invention Development Board} - \textsc{AI Technologies}}

\Description{\MarginText{\textsc{Sadaka-Reut}}\parbox{\langbox}{October 2018}$\cdotp$\ \ \textbf{Board of Directors Memeber} - \textsc{an Arab-Jewish Partnership Organizations}}

\Description{\MarginText{\textsc{ISCOL}}\parbox{\langbox}{October 2018}$\cdotp$\ \ \textbf{Committee Member} - \textsc{The Israel Seminar of Computational Linguistics}}

\Description{\MarginText{\textsc{Tel-Aviv Univ.}}\parbox{\langbox}{March 2015}$\cdotp$\ \ \textbf{Graduation With Honors} - \textsc{Cum Laude.}}

\Description{\MarginText{\textsc{HP Software R\&D}}\parbox{\langbox}{January 2015}$\cdotp$\ \ \textbf{Gold Innovator Award} - In recognition of outstanding innovation efforts.}

\vspace{-0.5em}

\Description{\parbox{\langbox}{August 2014}$\cdotp$\ \ \textbf{Innovator Award} - For making a valuable contribution through innovation.}


\Description{\MarginText{\textsc{Technion - IIT}}\parbox{\langbox}{Winter 2009 \\ Winter 2008}$\cdotp$\ \ \textbf{Excelled With Praise} - Dean's List.}

\vspace{0.5em}

%------------------------------------------------
%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS
%----------------------------------------------------------------------------------------
%\vspace{2em} % Extra space between major sections

%\Sectiontitle{Programming Skills}\vspace{1em}
%
%\Description{\MarginText{Languages}\textsc{TensorFlow}, Python, \textsc{Matlab}, \textsc{java}, SQL, C\#, Angular, \textsc{javascript} }
%
%\vspace{-0.5em} 
%
%\Description{\MarginText{Environments \& Tools}Windows, Unix, Git, \LaTeX, Weka, Amazon AWS}
%

%------------------------------------------------

%----------------------------------------------------------------------------------------
%	LANGUAGES
%----------------------------------------------------------------------------------------
%\vspace{1em}
%\Sectiontitle{Languages}\vspace{1em}
%%\newlength{\langbox} % Create a new length for the length of languages to keep them equally spaced
%\settowidth{\langbox}{English} % Length equals the length of "English" - if you have a longer language in your list put it here
%
%\Description{\parbox{\langbox}{\textsc{Arabic}}\ \ $\cdotp$\ \ \ Mother-tongue}
%
%\vspace{-0.5em} 
%
%\Description{\parbox{\langbox}{\textsc{Hebrew}}\ \ $\cdotp$\ \ \ Bilingual proficiency}
%
%\vspace{-0.5em} 
%
%\Description{\parbox{\langbox}{\textsc{English}}\ \ $\cdotp$\ \ \ Full professional proficiency}


%------------------------------------------------

%\Description{\MarginText{Interests}Piano\ \ $\cdotp$\ \ Cooking\ \ $\cdotp$\ \ Running\ \ $\cdotp$\ \ Chess\ \ $\cdotp$\ \ Dancing}

%----------------------------------------------------------------------------------------

%\date{}
\end{cv}

\end{document}
